Anony\emph{mice}d shareable data: Using \emph{mice} to create and analyze multiply imputed synthetic data sets

### 2021-10-27 manuscript/Manuscript.Rmd

After imputation, the quality of the synthetic data can be assessed using various utility measures. The simplest way to assess data quality is through visual inspection. However, visualizing more than two dimensions quickly becomes cumbersome, which makes it hard to assess the accuracy of multivariate relations. Trying to predict whether the data is observed or synthetic allows to get an intuition of the quality of the data. This procedure has been advanced by @snoke2018general, who proposed a measure of distributional similarity based on the mean squared error of propensity scores indicating class belonging for both observed and synthetic data. This method has been implemented in the `R`-package `synthpop` [@synthpop], who pioneered in the field of synthetic data generation in `R`.

>>>>

After imputation, the quality of the synthetic data can be assessed using various utility measures. The simplest way to assess data quality is through visual inspection. However, visualizing more than two dimensions quickly becomes cumbersome, which makes it hard to assess the accuracy of multivariate relations. Trying to predict whether the data is observed or synthetic allows to get an intuition of the quality of the data. This procedure has been advanced by @snoke2018general, who proposed a measure of distributional similarity based on the mean squared error of propensity scores indicating class belonging for both observed and synthetic data. Additionally, if one knows the analyses that will be carried out by the synthetic data users, it is possible to compare the results on the observed and the synthetic data, allowing to assess the accuracy of the synthetisation method. Both of these methods have been implemented in the `R`-package `synthpop` [@synthpop], who pioneered in the field of synthetic data generation in `R`.

### 2021-10-27 manuscript/Manuscript.tex

After imputation, the quality of the synthetic data can be assessed
using various utility measures. The simplest way to assess data quality
is through visual inspection. However, visualizing more than two
dimensions quickly becomes cumbersome, which makes it hard to assess the
accuracy of multivariate relations. Trying to predict whether the data
is observed or synthetic allows to get an intuition of the quality of
the data. This procedure has been advanced by \citet{snoke2018general},
who proposed a measure of distributional similarity based on the mean
squared error of propensity scores indicating class belonging for both
observed and synthetic data. This method has been implemented in the
\texttt{R}-package \texttt{synthpop} \citep{synthpop}, who pioneered in
the field of synthetic data generation in \texttt{R}.

>>>>

After imputation, the quality of the synthetic data can be assessed
using various utility measures. The simplest way to assess data quality
is through visual inspection. However, visualizing more than two
dimensions quickly becomes cumbersome, which makes it hard to assess the
accuracy of multivariate relations. Trying to predict whether the data
is observed or synthetic allows to get an intuition of the quality of
the data. This procedure has been advanced by \citet{snoke2018general},
who proposed a measure of distributional similarity based on the mean
squared error of propensity scores indicating class belonging for both
observed and synthetic data. Additionally, if one knows the analyses
that will be carried out by the synthetic data users, it is possible to
compare the results on the observed and the synthetic data, allowing to
assess the accuracy of the synthetisation method. Both of these methods
have been implemented in the \texttt{R}-package \texttt{synthpop}
\citep{synthpop}, who pioneered in the field of synthetic data
generation in \texttt{R}.
